---
title: "Downloading the Full IDS Data"
format: html
vignette: >
  %\VignetteIndexEntry{`wbids` Data Model}
  %\VignetteEngine{quarto::html}
  %\VignetteEncoding{UTF-8}
---

```{r setup}
library(wbids)
library(dplyr)
```

The `wbids` package provides two ways to download the complete International Debt Statistics  (IDS) dataset:

With `ids_bulk()`, you need to download and combine multiple Excel files:

```{r}
#| eval: false
# Step 1: Get list of available files
files <- ids_bulk_files()

# Step 2: Download each file
data_list <- lapply(files$file_url, ids_bulk)

# Step 3: Combine all data
full_data <- bind_rows(data_list)
```

With `ids_get_ed()`, you get everything in one step:

```{r ed-approach}
#| eval: false
full_data <- ids_get_ed("debt_statistics")
```

The `ids_get_ed()` function is faster because:

- Downloads one optimized file instead of multiple Excel files
- Uses Parquet format which is faster to read than Excel
- Data is already processed and ready to use

For most use cases, `ids_get_ed()` is the recommended approach due to its simplicity and performance benefits.
